---
title: "Bibmex MSCs-EVs"
author: "Gabriel"
date: "`r Sys.Date()`"
output: html_document
---

#Details
Articles retrieved from Web of Science database
Search query used:
  ((TS=(mesenchymal stromal cell)) OR TS=(MSCs) OR TS=(Mesenchymal stem cell)) AND (TS=(exosom*) OR TS=(micro vesicle*)) AND DT=(Article) AND PY=(2000-2024) AND LA=English

Data exported as plain text named download-##
  All search results exported to 10 files since the database only accepts 500 items per download
  
  
#Packages
```{r}
library(tidyverse)
library(bibliometrix)
```

#Data import
```{r}
df <- bibliometrix::convert2df(paste0("E:/Doutorado/Manuscritos/Bibliometrics/MSC-EVs/Data/", list.files("E:/Doutorado/Manuscritos/Bibliometrics/MSC-EVs/Data/")), dbsource = 'wos', format = 'plaintext')
```

#Data analysis
```{r}
b.analysis <- biblioAnalysis(df)

res.summ <- summary(b.analysis)

plot(x=b.analysis, k=10, pause=F)
```

##Citation analysis
```{r}
df$CR

cit.manuscript <- citations(df, field='article', sep=';')
cbind(cit.manuscript$Cited[1:10])

cit.author <- citations(df, field='author', sep=';')
cbind(cit.author$Cited[1:10])
```

The function localCitations generates the frequency table of the most local cited authors. Local citations measure how many times an author (or a document) included in this collection have been cited by other authors also in the collection.
```{r}
local.cit <- localCitations(df, sep = ';')
local.cit$Authors[1:10,]
local.cit$Papers[1:10,]
```

The function dominance calculates the authors’ dominance ranking as proposed by Kumar & Kumar, 2008.

Kumar, S., & Kumar, S. (2008). Collaboration in research productivity in oil seed research institutes of India. In Proceedings of Fourth International Conference on Webometrics, Informetrics and Scientometrics.
The Dominance Factor is a ratio indicating the fraction of multi-authored articles in which a scholar appears as the first author.
```{r}
author.dom <- dominance(b.analysis, k=10)
author.dom
```

```{r}
topAU <- authorProdOverTime(df, k = 15, graph = TRUE)
```


##Bibliographic network
```{r}

```

