---
title: "Bibmex MSCs-EVs"
author: "Gabriel"
date: "`r Sys.Date()`"
output: html_document
---

#Details
Articles retrieved from Web of Science database
Search query used:
  ((TS=(mesenchymal stromal cell)) OR TS=(MSCs) OR TS=(Mesenchymal stem cell)) AND (TS=(exosom*) OR TS=(micro vesicle*)) AND DT=(Article) AND PY=(2000-2024) AND LA=English

Data exported as plain text named download-##
  All search results exported to 10 files since the database only accepts 500 items per download
  
  
#Packages
```{r}
library(tidyverse)
library(bibliometrix)
```

#Data import
```{r}
df <- bibliometrix::convert2df(paste0("E:/Doutorado/Manuscritos/Bibliometrics/MSC-EVs/Data/", list.files("E:/Doutorado/Manuscritos/Bibliometrics/MSC-EVs/Data/")), dbsource = 'wos', format = 'plaintext')
```

#Data analysis
```{r}
b.analysis <- biblioAnalysis(df)

res.summ <- summary(b.analysis)

p1 <- plot(x=b.analysis, k=10, pause=F)

res.summ

pdf("../Results/Annual scientific production.pdf", width = 5, height = 4)
p1$AnnualScientProd
dev.off()

```

##Citation analysis
Análise dos artigos que foram citados pelos artigos presentes na coleção
```{r}
df$CR

cit.manuscript <- citations(df, field='article', sep=';')
cbind(cit.manuscript$Cited[1:10])
#Valadi et al é o artigo mais citado dentre dos artigos da coleção. Este artigo se refere a mecanismos de exossomos; não envolve MSCs e portanto não está presente na coleção.

cit.author <- citations(df, field='author', sep=';')
cbind(cit.author$Cited[1:10])

cit.manuscript$Cited %>% View()
```

The function localCitations generates the frequency table of the most local cited authors. Local citations measure how many times an author (or a document) included in this collection have been cited by other authors also in the collection.
```{r}
local.cit <- localCitations(df, sep = ';')
local.cit$Authors[1:10,]
local.cit$Papers[1:10,]

#local.cit$Papers %>% View()
```

The function dominance calculates the authors’ dominance ranking as proposed by Kumar & Kumar, 2008.

Kumar, S., & Kumar, S. (2008). Collaboration in research productivity in oil seed research institutes of India. In Proceedings of Fourth International Conference on Webometrics, Informetrics and Scientometrics.
The Dominance Factor is a ratio indicating the fraction of multi-authored articles in which a scholar appears as the first author.
```{r}
author.dom <- dominance(b.analysis, k=10)
author.dom
```

```{r}
topAU <- authorProdOverTime(df, k = 15, graph = TRUE)
topAU$graph
```


##Bibliographic network

cocMatrix is a general function to compute a bipartite network selecting one of the metadata attributes.

For example, to create a network Manuscript x Publication Source you have to use the field tag “SO”:
```{r}
manscrpt.pub <- cocMatrix(df, Field = "SO", sep = ";")
sort(Matrix::colSums(manscrpt.pub), decreasing = TRUE)[1:5]

author.network <- cocMatrix(df, Field = "AU", sep = ";")
sort(Matrix::colSums(author.network), decreasing = TRUE)[1:5]
```

```{r}
NetMatrix <- biblioNetwork(df, analysis = "coupling", network = "references", sep = ";")


#Scientific collaboration network is a network where nodes are authors and links are co-authorships as the latter is one of the most well-documented forms of scientific collaboration (Glanzel, 2004).
scientific.collaboration <- biblioNetwork(df, analysis = "collaboration", network = "authors", sep = ";")
netstat <- networkStat(scientific.collaboration)
summary(netstat)

networkPlot(scientific.collaboration,  normalize = "salton", weighted=NULL, n = 100, Title = "Scientific collaboration", type = "fruchterman", size=5,size.cex=T,remove.multiple=TRUE,labelsize=0.8,label.n=10,label.cex=F, )

networkPlot(scientific.collaboration)
networkPlot(scientific.collaboration, Title = 'Scientific collaboration', label.cex = F, n=50, halo = F, size = 5, remove.isolates = F, type = 'fruchterman')
```

##Country Scientific Collaboration
Como cada artigo traz a filiação com codigos sobrescritos, o numero de filiações é menor que o numero de autores
```{r}
country.collab <- metaTagExtraction(df, Field = "AU_CO", sep = ";")
country.collab <- metaTagExtraction(df, Field = "AU1_CO", sep = ";")


knitr::kable(table(unlist(strsplit(country.collab$AU_CO,';'))), 'latex')

country.contrib <- as.data.frame(table(unlist(strsplit(country.collab$AU_CO,';'))))
slice_max(country.contrib, order_by = Freq, n=10) %>% openxlsx::write.xlsx(., file='E:/Doutorado/Manuscritos/Bibliometrics/MSC-EVs/Results/Top10_contrib_countries.xlsx')
res.summ$MostProdCountries %>% openxlsx::write.xlsx(., file='E:/Doutorado/Manuscritos/Bibliometrics/MSC-EVs/Results/Top10_prod_countries.xlsx')



Net.country.collab <- biblioNetwork(country.collab, analysis = "collaboration", network = "countries", short = F)
# Plot the network
#Net.country.collab.plot <- 
networkPlot(Net.country.collab, n = 20, Title = "Country Collaboration", type = "circle", size=TRUE, remove.multiple=FALSE,labelsize=0.7, verbose=F)


collabByRegionPlot(as.matrix(Net.country.collab[c(1:25, 27:34), c(1:25, 27:34)]), edgesize = 4, label.cex = TRUE, labelsize=2.5,
weighted = TRUE, size=0.5, size.cex=TRUE, community.repulsion = 0)
```

##Keyword co-occurrences
```{r}
# Create keyword co-occurrences network
key.cooc <- biblioNetwork(df, analysis = "co-occurrences", network = "keywords", sep = ";")

# Plot the network
networkPlot(key.cooc, normalize = 'equivalence', weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size.cex = T, size = 25, edgesize = 5, label.cex = T, labelsize = 2)

```


##Co-Word Analysis: The conceptual structure of a field
```{r}
CS <- conceptualStructure(df,field="ID", method="CA", minDegree=4, clust=5, stemming=T, labelsize=10, documents=10)
CS$
```

#Thematic evolution
```{r}
theme.evo <- thematicEvolution(df, field = "ID", years=c(2012, 2017, 2021), stemming = T, minFreq = 5, synonyms = c("exosomes;exosome"), remove.terms = 'knee')
plotThematicEvolution(theme.evo$Nodes, theme.evo$Edges)
```

#Keywords
##Cumulative KW
```{r}
topKW <- KeywordGrowth(df, Tag = "ID", sep = ";", top=10, cdf=TRUE)
topKW

library(reshape2)
library(ggplot2)
df.topKW <- melt(topKW, id='Year')
ggplot(df.topKW,aes(Year, variable, color=variable))+
  geom_point()
```

```{r}
fieldByYear(df, timespan = c(2000,2024), synonyms = c("exosomes;exosome"))
```


